### 2017-01-07 paper/evaluation.tex
correcting myself: it's MEDIAN not AVG/MEAN, duhbash

We ran each subject's tests three times and grouped them according to
the time cost (in average): tests that run in less than a minute
(\emph{short} group), tests than run in one minute and less than five
minutes (\emph{medium} group), and tests that run in five (or more)
minutes (\emph{long} group). We based our classification from a
previous work \cite{gligoric-etal-issta2015} and added the
\emph{medium} group due to the variability of the time cost from
subjects out of the \emph{short} group. Figure~\ref{fig:rq1-boxplot}
shows the time cost distribution of each group: the \emph{short} group
is the most right skewed distribution with outliers closed to the
\emph{medium} group and 50\% of the subjects run in less than 15
seconds; the average from the \emph{medium} group is nearly two minutes
and most of the subjects run in less than four minutes; most of the
\emph{long} group runs in less than 25 minutes but has outliers that
require more than 50 minutes to execute. Figure~\ref{fig:rq1-barplot}
summarizes the proportion of subjects from each group.

>>>>

We ran each subject's tests three times and grouped them according to
the time cost (in average): tests that run in less than a minute
(\emph{short} group), tests than run in one minute and less than five
minutes (\emph{medium} group), and tests that run in five (or more)
minutes (\emph{long} group). We based our classification from a
previous work \cite{gligoric-etal-issta2015} and added the
\emph{medium} group due to the variability of the time cost from
subjects out of the \emph{short} group. Figure~\ref{fig:rq1-boxplot}
shows the time cost distribution of each group: the \emph{short} group
is the most right skewed distribution with outliers closed to the
\emph{medium} group and 50\% of the subjects run in less than 15
seconds; the median from the \emph{medium} group is nearly two minutes
and most of the subjects run in less than four minutes; most of the
\emph{long} group runs in less than 25 minutes but has outliers that
require more than 50 minutes to execute. Figure~\ref{fig:rq1-barplot}
summarizes the proportion of subjects from each group.
